---
title: "Upthat user manual"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Upthat user manual}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
# library(tidyverse)
```

# Introduction

This is the user manual of the Urban Health Impact Assessment Tool (upthat).
It focusses on using the tool via an interactive web application, currently hosted at https://atfutures.github.io/uta/.
For more advanced documentation, see the scenarios report and the adaptation manual.

# User interface options

# Outputs

# Running upthat locally

Upthat is a fully open and reproducible web application.
You can reproduce it on your computer on a local installation of R as follows:

```{r repro, eval=FALSE}
devtools::install_github("atfutures/upthat")
library(upthat)
upthat::runUpthat()
```

# Next steps



# References
